---
title: "P8105 HW5"
output: github_document
date: "2024-11-09"
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(dplyr)
library(broom)
library(purrr)
library(ggplot2)
library(knitr)
```

## Problem 1 

Creating function for birthdays. 
```{r}
birthdays_df <- expand_grid(
  group_size = 2:50,
  iter = 1:10000
)

check_duplicates <- function(n) {
  birthdays <- sample(1:365, n, replace = TRUE)
  any(duplicated(birthdays))
}

birthdays_df <- birthdays_df |> 
  mutate(duplicate = map(group_size, check_duplicates)) |> 
  unnest(duplicate) |> 
  group_by(group_size) |> 
  summarize(probability = mean(duplicate))
```

Visualizing the likelihood of two individuals with the same birthday. 

```{r}
ggplot(birthdays_df, aes(x = group_size, y = probability)) +
  geom_line() +
  labs(x = "Sample Size", y = "Probability of Same Birthday") +
  ggtitle("Problem #1: Birthdays") 
```


This plot indicates that as the sample size increases, the probability of two people sharing the same birthday increases. For example, if the group has about 25 people, we can observe that there is over 50% chance that two people will have the same birthday. 

## Problem 2 

```{r}
n <- 30
sigma <- 5
mu_values <- c(0, 1, 2, 3, 4, 5, 6)
n_sims <- 5000
```

```{r}
simulate_ttest <- function(mu = 0) {
  data <- tibble(x = rnorm(n, mean = mu, sd = sigma))
  ttest_result <- t.test(x~ 1, data = data)
  tidy(ttest_result) %>% 
    select(estimate, p.value) %>%
    mutate(mu = mu)
}
```

```{r}
results_list <- map(mu_values, function(mu) {
  replicate(n_sims, simulate_ttest(mu), simplify = FALSE)
})
```

```{r}
results_list <- lapply(results_list, as.data.frame)
```

```{r}
results_df <- results_list %>%
  map_dfr(~ .x, .id = "mu") %>%
  mutate(mu = as.numeric(mu),
         rejected = p.value < 0.05)
```

```{r}
power_df <- results_df %>%
  group_by(mu) %>%
  summarize(power = mean(rejected, na.rm = TRUE), .groups = "drop")
```

## Plot 1 
```{r}
ggplot(power_df, aes(x = mu, y = power)) +
  geom_point() +
  geom_line() +
  labs(x = "Mu", y = "Power") 
```

From our analysis, we can observe that as the effect size increases, the power of the test also increases. This means that as the true mean moves further away from the hypothesis, the sample will also be further from null value. Therefore, this indicates that we will reject the null hypothesis. 

```{r}
average_estimates <- results_df %>% 
  group_by(mu) %>% 
  summarize(avg_estimate = mean(estimate))

rejected_estimates <- results_df %>% 
  filter(p.value < 0.05, mu >= 0, mu <= 6) %>%  
  group_by(mu) %>% 
  summarize(avg_estimate_rejected = mean(estimate))

combined_estimates <- left_join(average_estimates, rejected_estimates, by = "mu")
```


## Plot 2: Combined All Tests & Rejected 
```{r}
ggplot(combined_estimates, aes(x = mu)) +
  geom_point(aes(y = avg_estimate, color = "All")) +
  geom_point(aes(y = avg_estimate_rejected, color = "Rejected")) + 
  geom_line(aes(y = avg_estimate, color = "All"), na.rm = TRUE) + 
  geom_line(aes(y = avg_estimate_rejected, color = "Rejected"), na.rm = TRUE) +  
  labs(x = "Mu", y = "Average Estimate", color = "Test Type")
```

This plot depicts two lines: the red line represents the  average estimate of ðœ‡Ì‚ (y)  and the value of ðœ‡(x). The blue line represents  the average estimate of ðœ‡Ì‚ in  which the null was rejected (y) and the value of ðœ‡ (x).From this plot we can observe that all tests runs continuously upward (overlapping the rejected line). However, the rejected showcases avg estimate further away from zero. 

## Plot 3: Average Mu_hat vs. True Mu 
```{r}
ggplot(average_estimates, aes(x = mu, y = avg_estimate)) +
  geom_point(alpha = 0.5) +
  stat_summary(fun = "mean", geom = "point", color = "red", size = 3) +
  geom_path() +
  labs(x = "True Value of Mu",
       y = "Average Estimate of Mu_hat",
       title = "Average Mu_hat vs. True Mu")
```

This graph depicts average estimate of ðœ‡Ì‚ over ðœ‡. 

## Problem 3 

Extracting the data. Making the city_state variable. To describe the raw data, we can see that there are a lot of homicides spanning across the US and a big discrepancy between closed/open cases with no arrest vs arrest. 

```{r}
homicide_df <- read.csv("data/homicide-data.csv")

city_summary <- homicide_df %>% 
  mutate(city_state = paste(city, state, sep = ", ")) %>% 
  group_by(city_state) %>% 
  summarize(
    total_homicides = n(),
    unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
  )
```

Let's examine Baltimore. 

```{r}
baltimore_test <- prop.test(
  x = city_summary %>% filter(city_state == "Baltimore, MD") %>% pull(unsolved_homicides),
  n = city_summary %>% filter(city_state == "Baltimore, MD") %>% pull(total_homicides)
)

baltimore_tidy <- broom::tidy(baltimore_test) %>% 
  select(estimate, conf.low, conf.high)
```


```{r}
city_props <- city_summary %>% 
  mutate(
    prop_test_results = map2(unsolved_homicides, total_homicides, ~prop.test(.x, .y))
  ) %>% 
  mutate(tidy_results = map(prop_test_results, broom::tidy)) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

## Table of Findings for Each City 

```{r}
city_props %>%
  mutate(
    estimate = round(estimate, 3),
    conf.low = round(conf.low, 3),
    conf.high = round(conf.high, 3)
  ) %>%
  select(city_state, estimate, conf.low, conf.high) %>%
  kable(
    col.names = c("City,State", "Estimated Proportion", "Lower Confidence Interval", "Upper Confidence Interval"),
    caption = "Proportion of Unsolved Homicides by City/State"
  )
```

```{r}
city_props %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(x = "City/ State", y = "Proportion of Unsolved Homicides") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

